Improving real-time trend estimates using local parametrisation of local polynomial regression filters

### 2024-04-02 paper/article_jos.tex
paer folder

\DeclareMathOperator{\e}{e}
\DeclareMathOperator{\Determinant}{det}
\renewcommand{\P}{\mathds{P}} %Apparement \P existe déjà ?
\newcommand\N{\mathds{N}}
\newcommand\Norm{\mathcal{N}}
\newcommand\R{\mathds{R}}
\newcommand\Z{\mathds{Z}}
\newcommand{\determinant}[1]{\Determinant\left(#1\right)}
%\newcommand\C{\mathds{C}}
%\newcommand\Z{\mathds{Z}}

@@

%\DefineBibliographyStrings{english}{andothers={et\addabbrvspace alii}}
\usepackage[authordate16,backend=biber,maxcitenames=2]{biblatex-chicago}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{biblatex}
\addbibresource{biblio.bib}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Improving real-time trend estimates using local parametrisation of local polynomial regression filters},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, frame hidden]}{\end{tcolorbox}}\fi

\setstretch{2}
\hypertarget{abstract}{%
\section*{Abstract}\label{abstract}}
\addcontentsline{toc}{section}{Abstract}

@@

\hypertarget{introduction}{%
\section*{Introduction}\label{introduction}}
\addcontentsline{toc}{section}{Introduction}

@@

Using local polynomial regression, \textcite{proietti2008} developed
general class of symmetric and asymmetric moving averages. In
particular, it makes possible to reproduce Henderson's symmetric filter
and Musgrave's asymmetric filters. However, these methods have two
drawbacks. Firstly, the phase shift (i.e.~the delay in detecting turning
points) is not directly controlled. Secondly, asymmetric filters depend
on a parameter that is generally estimated over the whole series using
assumptions that may be wrong locally. The aim of this study is to
propose extensions to the \textcite{proietti2008} class of filters in
order to take these shortcomings into account. The extensions have been
implemented in the \faIcon{r-project} \texttt{rjd3filters} package
(available at \url{https://github.com/rjdemetra/rjd3filters}) and are
therefore easily reusable.

@@

\hypertarget{sec-propMM}{%
\section{Some properties on moving averages}\label{sec-propMM}}

@@

Let \(p\) et \(f\) two integers, a moving average
\(M_{\boldsymbol\theta}\) or \(M\) is defined by a set of coefficients
\(\boldsymbol\theta=\begin{pmatrix}\theta_{-p}\\\vdots\\\theta_{f}\end{pmatrix}\)
such as for all time series \(X_t\): \[
M_{\boldsymbol\theta}(X_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}.
\]

@@

\hypertarget{subsec:gain-deph}{%
\subsection{Gain and phase shift functions}\label{subsec:gain-deph}}

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{img/filters_used/musgrave.pdf}

@@

\end{figure}

\hypertarget{desirable-properties-of-a-moving-average}{%
\subsection{Desirable properties of a moving
average}\label{desirable-properties-of-a-moving-average}}

@@

\hypertarget{trend-preservation}{%
\subsubsection{Trend preservation}\label{trend-preservation}}

@@

\hypertarget{noise-reduction}{%
\subsubsection{Noise reduction}\label{noise-reduction}}

@@

\hypertarget{sec-mmasym}{%
\subsection{Real-time estimation and asymmetric moving
average}\label{sec-mmasym}}

\hypertarget{sec-mmetprev}{%
\subsubsection{Asymmetric moving averages and
forecasts}\label{sec-mmetprev}}

@@

\hypertarget{subsec:crit-qual}{%
\subsubsection{Quality indicators for asymmetric moving
averages}\label{subsec:crit-qual}}

@@

\textcite{ch15HBSA} propose a general approach to derive linear filters,
based on an optimisation problem involving three criteria:
\emph{Fidelity} (\(F_g\)), \emph{Smoothness} (\(S_g\)) and
\emph{Timeliness} (\(T_g\)). Fidelity can be directly linked to the
reduction in variance created by the filter, and timeliness to the
notion of phase shift, which again we want to be low. This method can be
used in\faIcon{r-project} with the function
\texttt{rjd3filters::fst\_filter()}.

\textcite{trilemmaWMR2019} propose an approach based on the
decomposition of the mean squared error between the symmetric and the
asymmetric filter in four quantities: \emph{Accuracy} (\(A_w\)),
\emph{Timeliness} (\(T_w\)), \emph{Smoothness} (\(S_w\)) and
\emph{Residual} (\(R_w\)). A simplified version of this method can be
used in \faIcon{r-project} with the function
\texttt{rjd3filters::dfa\_filter()}.

\begin{table}[!h]
\caption{\label{tab-QC} Quality criteria for asymmetric filters ($q=0,1,2$) computed by local polynomials using the Henderson kernel with $h=6$ and $R=3,5$.}
{\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{ccc}
\toprule
Code & Description & Formula\\
\midrule
$b_c$ & Constant bias & $\sum_{k=-p}^{+f}\theta_{k}-1$\\
$b_l$ & Linear bias & $\sum_{k=-p}^{+f}k\theta_{k}$\\
$b_q$ & Quadratic bias & $\sum_{k=-p}^{+f}k^{2}\theta_{k}$\\
$F_g$ & Variance reduction / Fidelity (Guggemos) & $\sum_{k=-p}^{+f}\theta_{k}^{2}$\\
$S_g$ & Smoothness (Guggemos) & $\sum_{j}(\nabla^{3}\theta_{j})^{2}$\\
\addlinespace
$T_g$ & Timeliness (Guggemos) & $\int_{0}^{\omega_1}\rho_{\boldsymbol\theta}(\omega)\sin(\varphi_{\boldsymbol\theta}(\omega))^{2}\ud\omega$\\
$A_w$ & Accuracy (Wildi) & $2\int_0^{\omega_1}\left(\rho_{s}(\omega)-\rho_{\boldsymbol\theta}(\omega)\right)^{2}h(\omega)\ud\omega$\\
$T_w$ & Timeliness (Wildi) & $8\int_0^{\omega_1} \rho_{s}(\omega)\rho_{\boldsymbol\theta}(\omega)\sin^{2}\left(\frac{\varphi_s(\omega)-\varphi_{\boldsymbol\theta}(\omega)}{2}\right)h(\omega)\ud\omega$\\
$S_w$ & Smoothness (Wildi) & $2\int_{\omega_1}^{\pi}\left(\rho_{s}(\omega)-\rho_{\boldsymbol\theta}(\omega)\right)^{2}h(\omega)\ud\omega$\\
$R_w$ & Residual (Wildi) & $8\int_{\omega_1}^{\pi} \rho_{s}(\omega)\rho_{\boldsymbol\theta}(\omega)\sin^{2}\left(\frac{\varphi_s(\omega)-\varphi_{\boldsymbol\theta}(\omega)}{2}\right)h(\omega)\ud\omega$\\
\bottomrule
\end{tabular}}}

@@

\textit{$h$ is the spectral density of the input series, considered to be that of white noise ($h_{WN}(x)=1$) or a random walk ($h_{RW}(x)=\frac{1}{2(1-\cos(x))}$).}
\end{table}

\hypertarget{sec-nonparamreg}{%
\section{Non-parametric regression and local polynomial
regression}\label{sec-nonparamreg}}

Many trend-cycle extraction methods are based on non-parametric
regressions, which are particularly flexible because they do not assume
any predetermined dependency in the predictors. In practice, local
regressions can be used. More specifically, consider a set of points
\((x_i,y_i)_{1\leq i\leq n}\). Non-parametric regression involves
assuming that there exists a function \(\mu\), to be estimated, such
that \(y_i=\mu(x_i)+\varepsilon_i\) with \(\varepsilon_i\) an error
term. According to Taylor's theorem, for any point \(x_0\), if \(\mu\)
is differentiable \(d\) times, then:
\begin{equation}\protect\hypertarget{eq-taylor}{}{
\forall x \::\:\mu(x) = \mu(x_0) + \mu'(x_0)(x-x_0)+\dots +
\frac{\mu^{(d)}(x_0)}{d!}(x-x_0)^d+R_d(x),
}\label{eq-taylor}\end{equation} where \(R_d\) is a negligible residual
term in the neighbourhood of \(x_0\). In a neighbourhood \(h(x_0)\)
around \(x_0\), \(\mu\) can be approximated by a polynomial of degree
\(d\). The quantity \(h(x_0)\) is called the \emph{bandwidth}. If
\(\varepsilon_i\) is white noise, then we can estimate by least squares
\(\mu(x_0)\) using the observations which are in
\(\left[x_0-h(x_0),x_0+h(x_0)\right]\).

In practice, this means assuming that the trend is locally polynomial.
Various estimation methods can be used to derive symmetrical and
asymmetrical moving averages.\\
\textcite{GrayThomson1996} propose a complete statistical framework
which makes it possible, in particular, to model the error in
approximating the trend by local polynomials. However, as the
specification of this error is generally complex, simpler models may be
preferred, such as that of \textcite{proietti2008}.\\
Finally, \textcite{dagumbianconcini2008} propose a similar modelling of
the trend-cycle but using the theory of Hilbert spaces with reproducing
kernels for estimation, which has the particular advantage of
facilitating the calculation of different moving averages at different
time frequencies. This method can be used in\faIcon{r-project} with the
function \texttt{rjd3filters::rkhs\_filter()}.

\hypertarget{symmetric-moving-averages-and-local-polynomial-regression}{%
\subsection{Symmetric moving averages and local polynomial
regression}\label{symmetric-moving-averages-and-local-polynomial-regression}}

@@

To estimate \(\boldsymbol \beta\) we need \(2h+1\geq d+1\) and the
estimation is made by weighted least squares (WLS), which is equivalent
to minimising the following objective function: \[
S(\hat{\beta}_{0},\dots,\hat{\beta}_{d})=\sum_{j=-h}^{h}\kappa_{j}(y_{t+j}-\hat{\beta}_{0}-\hat{\beta}_{1}j-\dots-\hat{\beta}_{d}j^{d})^{2}.
\] where \(\kappa_j\) is a set of weights called \emph{kernel}. We have
\(\kappa_j\geq 0:\kappa_{-j}=\kappa_j\), and with
\(\boldsymbol K=diag(\kappa_{-h},\dots,\kappa_{h})\), the estimate of
\(\boldsymbol \beta\) can be written as
\(\hat{\boldsymbol\beta}=(\boldsymbol X'\boldsymbol K\boldsymbol X)^{-1}\boldsymbol X'\boldsymbol K\boldsymbol y.\)
With \(\boldsymbol e_1=\begin{pmatrix}1 \\0 \\\vdots\\0 \end{pmatrix}\),
the estimate of the trend is:
\begin{equation}\protect\hypertarget{eq-mmsym}{}{
\hat{m}_{t}=\boldsymbol e_{1}\hat{\boldsymbol \beta}=\boldsymbol \theta'\boldsymbol y=\sum_{j=-h}^{h}\theta_{j}y_{t-j}\text{ with }\boldsymbol \theta=\boldsymbol K\boldsymbol X(\boldsymbol X'\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{1}.
}\label{eq-mmsym}\end{equation} To conclude, the estimate of the trend
\(\hat{m}_{t}\) can be obtained applying the symmetric filter
\(\boldsymbol \theta\) to \(y_t\) (\(\boldsymbol \theta\) is symmetric
due to the symmetry of the kernel weights \(\kappa_j\)). Moreover,
\(\boldsymbol X'\boldsymbol \theta=\boldsymbol e_{1}\) so: \[
\sum_{j=-h}^{h}\theta_{j}=1,\quad\forall r\in\left\llbracket 1,d\right\rrbracket:\sum_{j=-h}^{h}j^{r}\theta_{j}=0.
\] Hence, the filter \(\boldsymbol w\) preserve deterministic polynomial
of order \(d\).

@@

\hypertarget{sec-lppasymf}{%
\subsection{Asymmetric moving averages and local polynomial
regression}\label{sec-lppasymf}}

@@

The initial series is modelled here as:
\begin{equation}\protect\hypertarget{eq-lpgeneralmodel}{}{
\boldsymbol y=\boldsymbol U \boldsymbol \gamma+\boldsymbol Z\boldsymbol \delta+\boldsymbol \varepsilon,\quad
\boldsymbol \varepsilon\sim\mathcal{N}(0,\boldsymbol D).
}\label{eq-lpgeneralmodel}\end{equation} where
\([\boldsymbol U,\boldsymbol Z]\) is of full rank and forms a subset of
the columns of \(X\). The objective is to find a filter
\(\boldsymbol v\) that minimises the mean square error of revision (to
the symmetric filter \(\boldsymbol \theta\)) under certain constraints.
These constraints are represented by the matrix
\(\boldsymbol U=\begin{pmatrix}\boldsymbol U_{p}\\\boldsymbol U_{f}\end{pmatrix}\):
\(\boldsymbol U_p'\boldsymbol v=\boldsymbol U'\boldsymbol \theta\) (with
\(\boldsymbol U_p\) the matrix \((h+q+1)\times (d+1)\) which contains
the observations of the matrix \(U\) known during estimation by the
asymmetric filter). The problem is equivalent to finding \(v\) which
minimises: \begin{equation}\protect\hypertarget{eq-lppasym}{}{
\varphi(\boldsymbol v)=
\underbrace{
  \underbrace{(\boldsymbol v-\boldsymbol \theta_{p})'\boldsymbol D_{p}(\boldsymbol v-\boldsymbol \theta_{p})+
  \boldsymbol \theta_{f}'\boldsymbol D_{f}\boldsymbol \theta_{f}}_\text{revision error variance}+
  \underbrace{[\boldsymbol \delta'(\boldsymbol Z_{p}'\boldsymbol v-\boldsymbol Z'\boldsymbol \theta)]^{2}}_{bias^2}
}_\text{mean square revision error}+
\underbrace{2\boldsymbol l'(\boldsymbol U_{p}'\boldsymbol v-\boldsymbol U'\boldsymbol \theta)}_{\text{constraints}}.
}\label{eq-lppasym}\end{equation} where \(\boldsymbol l\) is a vector of
Lagrange multipliers.

@@

When \(\boldsymbol U=\begin{pmatrix}1\\\vdots\\1\end{pmatrix}\),
\(\boldsymbol Z=\begin{pmatrix}-h\\\vdots\\+h\end{pmatrix}\),
\(\boldsymbol \delta=\delta_1\), \(\boldsymbol D=\sigma^2\boldsymbol I\)
and when the symmetric filter is the Henderson filter, we find the
asymmetric Musgrave filters (using the Henderson kernel). This filter
assumes that, for real-time estimation, the data is generated by a
linear process and that the asymmetric filters preserve the constants
(\(\sum v_i=\sum \theta_i=1\)). These asymmetric filters depend on the
ratio \(\lvert\delta_1/\sigma\rvert\), which, assuming that the trend is
linear and the bias constant, can be linked to the I-C ratio
\(R=\frac{\bar{I}}{\bar{C}}=\frac{\sum\lvert I_t-I_{t-1}\rvert}{\sum\lvert C_t-C_{t-1}\rvert}\):
\(\delta_1/\sigma=2/(R\sqrt{\pi})\). This ratio is used in particular in
X-13ARIMA to determine the length of the Henderson filter. For monthly
data:

@@

\hypertarget{sec-localic}{%
\subsection{Local parameterisation of asymmetric
filters}\label{sec-localic}}

@@

{\centering \includegraphics[width=0.9\textwidth,height=\textheight]{img/filters_used/mm_penteconcavite.pdf}

@@

\end{figure}

@@

\begin{figure}

\caption{\label{fig-mmpenteconcac-ex}Comparison of the estimates of
\(|\delta_1/\sigma|\) with a local estimator and global estimator (with
IC ratio) on a simulated series, the vertical lines being the simulated
turning points.}\begin{minipage}[t]{\linewidth}
\subcaption{\label{fig-mmpenteconcac-ex-1}Symmetric moving average used
for \(\hat \delta_1\).}

{\centering

\raisebox{-\height}{

>>>>

\DeclareMathOperator{\e}{e}
\DeclareMathOperator{\Determinant}{det}
\renewcommand{\P}{\mathds{P}} %Apparement \P existe déjà ?
\newcommand\N{\mathds{N}}
\newcommand\Norm{\mathcal{N}}
\newcommand\R{\mathds{R}}
\newcommand\Z{\mathds{Z}}
\newcommand\transp[1]{{#1}^T}
%\newcommand\C{\mathds{C}}
%\newcommand\Z{\mathds{Z}}

@@

%\DefineBibliographyStrings{english}{andothers={et\addabbrvspace alii}}
\usepackage[authordate16,backend=biber,maxcitenames=2]{biblatex-chicago}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{biblatex}
\addbibresource{biblio.bib}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Improving real-time trend estimates using local parametrisation of local polynomial regression filters},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{document}
\maketitle

\setstretch{2}
\section*{Abstract}\label{abstract}
\addcontentsline{toc}{section}{Abstract}

@@

\section{Introduction}\label{introduction}

@@

Using local polynomial regression, \textcite{proietti2008} developed
general class of symmetric and asymmetric moving averages. In
particular, it makes possible to reproduce Henderson's symmetric filter
and Musgrave's asymmetric filters. However, these methods have two
drawbacks. Firstly, the phase shift (i.e.~the delay in detecting turning
points) is not directly controlled. Secondly, asymmetric filters depend
on a parameter that is generally estimated over the whole series using
assumptions that may be wrong locally. The aim of this study is to
propose extensions to the \textcite{proietti2008} class of filters in
order to take these shortcomings into account. The extensions have been
implemented in the R \texttt{rjd3filters} package (available at
\url{https://github.com/rjdemetra/rjd3filters}) and are therefore easily
reusable.

@@

\section{Some properties on moving averages}\label{sec-propMM}

@@

Let \(p\) et \(f\) two integers, a moving average
\(M_{\boldsymbol\theta}\) or \(M\) is defined by a set of coefficients
\(\boldsymbol\theta=\transp{\begin{pmatrix}\theta_{-p}&\cdots&\theta_{f}\end{pmatrix}}\)
such as for all time series \(X_t\): \[
M_{\boldsymbol\theta}(X_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}.
\]

@@

\subsection{Gain and phase shift functions}\label{subsec:gain-deph}

@@

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{img/filters_used/musgrave.pdf}

@@

\end{figure}%

\subsection{Desirable properties of a moving
average}\label{desirable-properties-of-a-moving-average}

@@

\subsubsection{Trend preservation}\label{trend-preservation}

@@

\subsubsection{Noise reduction}\label{noise-reduction}

@@

\subsection{Real-time estimation and asymmetric moving
average}\label{sec-mmasym}

\subsubsection{Asymmetric moving averages and
forecasts}\label{sec-mmetprev}

@@

\subsubsection{Quality indicators for asymmetric moving
averages}\label{subsec:crit-qual}

@@

\textcite{ch15HBSA} propose a general approach to derive linear filters,
based on an optimisation problem involving three criteria:
\emph{Fidelity} (\(F_g\)), \emph{Smoothness} (\(S_g\)) and
\emph{Timeliness} (\(T_g\)). Fidelity can be directly linked to the
reduction in variance created by the filter, and timeliness to the
notion of phase shift, which again we want to be low. This method can be
used inR with the function \texttt{rjd3filters::fst\_filter()}.

\textcite{trilemmaWMR2019} propose an approach based on the
decomposition of the mean squared error between the symmetric and the
asymmetric filter in four quantities: \emph{Accuracy} (\(A_w\)),
\emph{Timeliness} (\(T_w\)), \emph{Smoothness} (\(S_w\)) and
\emph{Residual} (\(R_w\)). A simplified version of this method can be
used in R with the function \texttt{rjd3filters::dfa\_filter()}.

\begin{table}

\caption{\label{tab-QC} Quality criteria for asymmetric filters ($q=0,1,2$) computed by local polynomials using the Henderson kernel with $h=6$ and $R=3,5$.}

\centering{

[!h]

{\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{ccc}
\toprule
Code & Description & Formula\\
\midrule
$b_c$ & Constant bias & $\sum_{k=-p}^{+f}\theta_{k}-1$\\
$b_l$ & Linear bias & $\sum_{k=-p}^{+f}k\theta_{k}$\\
$b_q$ & Quadratic bias & $\sum_{k=-p}^{+f}k^{2}\theta_{k}$\\
$F_g$ & Variance reduction / Fidelity (Guggemos) & $\sum_{k=-p}^{+f}\theta_{k}^{2}$\\
$S_g$ & Smoothness (Guggemos) & $\sum_{j}(\nabla^{3}\theta_{j})^{2}$\\
\addlinespace
$T_g$ & Timeliness (Guggemos) & $\int_{0}^{\omega_1}\rho_{\boldsymbol\theta}(\omega)\sin(\varphi_{\boldsymbol\theta}(\omega))^{2}\ud\omega$\\
$A_w$ & Accuracy (Wildi) & $2\int_0^{\omega_1}\left(\rho_{s}(\omega)-\rho_{\boldsymbol\theta}(\omega)\right)^{2}h(\omega)\ud\omega$\\
$T_w$ & Timeliness (Wildi) & $8\int_0^{\omega_1} \rho_{s}(\omega)\rho_{\boldsymbol\theta}(\omega)\sin^{2}\left(\frac{\varphi_s(\omega)-\varphi_{\boldsymbol\theta}(\omega)}{2}\right)h(\omega)\ud\omega$\\
$S_w$ & Smoothness (Wildi) & $2\int_{\omega_1}^{\pi}\left(\rho_{s}(\omega)-\rho_{\boldsymbol\theta}(\omega)\right)^{2}h(\omega)\ud\omega$\\
$R_w$ & Residual (Wildi) & $8\int_{\omega_1}^{\pi} \rho_{s}(\omega)\rho_{\boldsymbol\theta}(\omega)\sin^{2}\left(\frac{\varphi_s(\omega)-\varphi_{\boldsymbol\theta}(\omega)}{2}\right)h(\omega)\ud\omega$\\
\bottomrule
\end{tabular}}}

@@

\textit{$h$ is the spectral density of the input series, considered to be that of white noise ($h_{WN}(x)=1$) or a random walk ($h_{RW}(x)=\frac{1}{2(1-\cos(x))}$).}

\end{table}%

\section{Non-parametric regression and local polynomial
regression}\label{sec-nonparamreg}

Many trend-cycle extraction methods are based on non-parametric
regressions, which are particularly flexible because they do not assume
any predetermined dependency in the predictors. In practice, local
regressions can be used. More specifically, consider a set of points
\((x_i,y_i)_{1\leq i\leq n}\). Non-parametric regression involves
assuming that there exists a function \(\mu\), to be estimated, such
that \(y_i=\mu(x_i)+\varepsilon_i\) with \(\varepsilon_i\) an error
term. According to Taylor's theorem, for any point \(x_0\), if \(\mu\)
is differentiable \(d\) times, then:
\begin{equation}\phantomsection\label{eq-taylor}{
\forall x \::\:\mu(x) = \mu(x_0) + \mu'(x_0)(x-x_0)+\dots +
\frac{\mu^{(d)}(x_0)}{d!}(x-x_0)^d+R_d(x),
}\end{equation} where \(R_d\) is a negligible residual term in the
neighbourhood of \(x_0\). In a neighbourhood \(h(x_0)\) around \(x_0\),
\(\mu\) can be approximated by a polynomial of degree \(d\). The
quantity \(h(x_0)\) is called the \emph{bandwidth}. If \(\varepsilon_i\)
is white noise, then we can estimate by least squares \(\mu(x_0)\) using
the observations which are in \(\left[x_0-h(x_0),x_0+h(x_0)\right]\).

In practice, this means assuming that the trend is locally polynomial.
Various estimation methods can be used to derive symmetrical and
asymmetrical moving averages.\\
\textcite{GrayThomson1996} propose a complete statistical framework
which makes it possible, in particular, to model the error in
approximating the trend by local polynomials. However, as the
specification of this error is generally complex, simpler models may be
preferred, such as that of \textcite{proietti2008}.\\
Finally, \textcite{dagumbianconcini2008} propose a similar modelling of
the trend-cycle but using the theory of Hilbert spaces with reproducing
kernels for estimation, which has the particular advantage of
facilitating the calculation of different moving averages at different
time frequencies. This method can be used inR with the function
\texttt{rjd3filters::rkhs\_filter()}.

\subsection{Symmetric moving averages and local polynomial
regression}\label{symmetric-moving-averages-and-local-polynomial-regression}

@@

To estimate \(\boldsymbol \beta\) we need \(2h+1\geq d+1\) and the
estimation is made by weighted least squares (WLS), which is equivalent
to minimising the following objective function: \[
S(\hat{\beta}_{0},\dots,\hat{\beta}_{d})=\sum_{j=-h}^{h}\kappa_{j}(y_{t+j}-\hat{\beta}_{0}-\hat{\beta}_{1}j-\dots-\hat{\beta}_{d}j^{d})^{2}.
\] where \(\kappa_j\) is a set of weights called \emph{kernel}. We have
\(\kappa_j\geq 0:\kappa_{-j}=\kappa_j\), and with
\(\boldsymbol K=diag(\kappa_{-h},\dots,\kappa_{h})\), the estimate of
\(\boldsymbol \beta\) can be written as
\(\hat{\boldsymbol\beta}=(\boldsymbol X'\boldsymbol K\boldsymbol X)^{-1}\boldsymbol X'\boldsymbol K\boldsymbol y.\)
With
\(\boldsymbol e_1=\transp{\begin{pmatrix}1 &0 &\cdots&0 \end{pmatrix}}\),
the estimate of the trend is:
\begin{equation}\phantomsection\label{eq-mmsym}{
\hat{m}_{t}=\boldsymbol e_{1}\hat{\boldsymbol \beta}=\boldsymbol \theta'\boldsymbol y=\sum_{j=-h}^{h}\theta_{j}y_{t-j}\text{ with }\boldsymbol \theta=\boldsymbol K\boldsymbol X(\boldsymbol X'\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{1}.
}\end{equation} To conclude, the estimate of the trend \(\hat{m}_{t}\)
can be obtained applying the symmetric filter \(\boldsymbol \theta\) to
\(y_t\) (\(\boldsymbol \theta\) is symmetric due to the symmetry of the
kernel weights \(\kappa_j\)). Moreover,
\(\boldsymbol X'\boldsymbol \theta=\boldsymbol e_{1}\) so: \[
\sum_{j=-h}^{h}\theta_{j}=1,\quad\forall r\in\left\llbracket 1,d\right\rrbracket:\sum_{j=-h}^{h}j^{r}\theta_{j}=0.
\] Hence, the filter \(\boldsymbol w\) preserve deterministic polynomial
of order \(d\).

@@

\subsection{Asymmetric moving averages and local polynomial
regression}\label{sec-lppasymf}

@@

The initial series is modelled here as:
\begin{equation}\phantomsection\label{eq-lpgeneralmodel}{
\boldsymbol y=\boldsymbol U \boldsymbol \gamma+\boldsymbol Z\boldsymbol \delta+\boldsymbol \varepsilon,\quad
\boldsymbol \varepsilon\sim\mathcal{N}(0,\boldsymbol D).
}\end{equation} where \([\boldsymbol U,\boldsymbol Z]\) is of full rank
and forms a subset of the columns of \(X\). The objective is to find a
filter \(\boldsymbol v\) that minimises the mean square error of
revision (to the symmetric filter \(\boldsymbol \theta\)) under certain
constraints. These constraints are represented by the matrix
\(\boldsymbol U=\transp{\begin{pmatrix} \transp{\boldsymbol U_{p}}& \transp{\boldsymbol U_{f}}\end{pmatrix}}\):
\(\boldsymbol U_p'\boldsymbol v=\boldsymbol U'\boldsymbol \theta\) (with
\(\boldsymbol U_p\) the matrix \((h+q+1)\times (d+1)\) which contains
the observations of the matrix \(U\) known during estimation by the
asymmetric filter). The problem is equivalent to finding \(v\) which
minimises: \begin{equation}\phantomsection\label{eq-lppasym}{
\varphi(\boldsymbol v)=
\underbrace{
  \underbrace{(\boldsymbol v-\boldsymbol \theta_{p})'\boldsymbol D_{p}(\boldsymbol v-\boldsymbol \theta_{p})+
  \boldsymbol \theta_{f}'\boldsymbol D_{f}\boldsymbol \theta_{f}}_\text{revision error variance}+
  \underbrace{[\boldsymbol \delta'(\boldsymbol Z_{p}'\boldsymbol v-\boldsymbol Z'\boldsymbol \theta)]^{2}}_{bias^2}
}_\text{mean square revision error}+
\underbrace{2\boldsymbol l'(\boldsymbol U_{p}'\boldsymbol v-\boldsymbol U'\boldsymbol \theta)}_{\text{constraints}}.
}\end{equation} where \(\boldsymbol l\) is a vector of Lagrange
multipliers.

@@

When \(\boldsymbol U=\transp{\begin{pmatrix}1&\cdots&1\end{pmatrix}}\),
\(\boldsymbol Z=\transp{\begin{pmatrix}-h&\cdots&+h\end{pmatrix}}\),
\(\boldsymbol \delta=\delta_1\), \(\boldsymbol D=\sigma^2\boldsymbol I\)
and when the symmetric filter is the Henderson filter, we find the
asymmetric Musgrave filters (using the Henderson kernel). This filter
assumes that, for real-time estimation, the data is generated by a
linear process and that the asymmetric filters preserve the constants
(\(\sum v_i=\sum \theta_i=1\)). These asymmetric filters depend on the
ratio \(\lvert\delta_1/\sigma\rvert\), which, assuming that the trend is
linear and the bias constant, can be linked to the I-C ratio
\(R=\frac{\bar{I}}{\bar{C}}=\frac{\sum\lvert I_t-I_{t-1}\rvert}{\sum\lvert C_t-C_{t-1}\rvert}\):
\(\delta_1/\sigma=2/(R\sqrt{\pi})\). This ratio is used in particular in
X-13ARIMA to determine the length of the Henderson filter. For monthly
data:

@@

\subsection{Local parameterisation of asymmetric
filters}\label{sec-localic}

@@

\centering{

\includegraphics[width=0.9\textwidth,height=\textheight]{img/filters_used/mm_penteconcavite.pdf}

@@

\end{figure}%

@@

\caption{\label{fig-mmpenteconcac-ex}Comparison of the estimates of
\(|\delta_1/\sigma|\) with a local estimator and global estimator (with
IC ratio) on a simulated series, the vertical lines being the simulated
turning points.}

\begin{minipage}{\linewidth}

\subcaption{\label{fig-mmpenteconcac-ex-1}Symmetric moving average used
for \(\hat \delta_1\).}

\centering{

\includegraphics[width=0.9\textwidth,height=\textheight]{img/filters_used/mm_penteconcavite_ex.pdf}
